%\documentclass[numberedappendix]{emulateapj}
\documentclass[letterpaper,12pt,preprint]{aastex}

\input{preamble.tex}

\begin{document}

\title{The stellar halo of the Milky Way and globular cluster debris I: predictions for kinematic structure}
\author{Adrian~M.~Price-Whelan\altaffilmark{\pu,\adrn},
        Oleg Gnedin\altaffilmark{\umich},
        Kathryn V. Johnston\altaffilmark{\colum},
        David N. Spergel\altaffilmark{\cca,\pu}
%       Hans-Walter~Rix\altaffilmark{\mpia}
}

% Affiliations
\newcommand{\pu}{1}
\newcommand{\adrn}{2}
\newcommand{\umich}{3}
\newcommand{\colum}{4}
\newcommand{\cca}{5}
%\newcommand{\mpia}{6}

\altaffiltext{\pu}{Department of Astrophysical Sciences,
                   Princeton University, Princeton, NJ 08544, USA}
\altaffiltext{\adrn}{To whom correspondence should be addressed:
                     \texttt{adrn@princeton.edu}}

% TODO: michigan
\altaffiltext{\umich}{Department of Astronomy ??,
                      University of Michigan,
                      USA}
\altaffiltext{\colum}{Department of Astronomy,
                      Columbia University,
                      550 W 120th St.,
                      New York, NY 10027, USA}
% TODO: Simons
\altaffiltext{\cca}{Simons Center for Computational Astrophysics,
                      New York, NY XXX, USA}
%\altaffiltext{\mpia}{Max-Planck-Institut f\"ur Astronomie,
%                    K\"onigstuhl 17, D-69117 Heidelberg, Germany}

\begin{abstract}
% Context
Milky Way halo globular clusters probably accreted -- opportunity to study accretion history, blah blah.


Recent work studying the detailed chemical abundances of Milky Way halo stars
and the kinematic evolution of globular clusters suggest that (1) a significant
fraction of the stellar halo around the Milky Way could be composed of disrupted
globular clusters, and, consequently, that (2) the present globular cluster
population may be a small fraction ($<$5\%) of the initial population.
These suggestions make strong predictions about the structure---in kinematics
and chemistry---of halo stars that depend strongly on the origins of the initial
globular cluster system.
% Aims
Here we generate a set of mock stellar halos formed from disrupted globular
clusters with a range of formation scenarios that all broadly reproduce the
present-day spatial distribution and mass function of the remnant cluster
population.
We use these halos to predict the kinematic clustering of halo stars and the
expected number of thin stellar streams around the Milky Way for each of the
explored scenarios.
% Methods
We consider two main classes of initial conditions: (1) all accreted, in which
all globular clusters were deposited early on through mergers with other
galaxies, and (2) all formed in situ, in which all globular clusters formed
early on in the Galaxy.
For each, we consider cluster orbits drawn from isotropic, radially-anisotropic,
and tangentially-anisotropic distribution functions.
% Results
We find that the end-of-Gaia kinematic measurements for XX stars within XX kpc
of the Sun will distinguish the scenarios considered in this work.
We also predict that within XX kpc of the Galactic center, there are XX thin,
recently fully-disrupted globular-cluster streams.
Of these, XX have high enough surface brightness to have already been detected,
in agreement with the number of thin streams discovered thus far.

\end{abstract}

\keywords{
  Galaxy: halo
  ---
  globular clusters: general
  ---
  stars: kinematics and dynamics
  ---
  Galaxy: structure
  ---
  Galaxy: kinematics and dynamics
}

\section{Introduction}\label{sec:introduction}

\section{Conclusions}\label{sec:conclusions}

\acknowledgements
This research made use of
Astropy, a community-developed core Python package for Astronomy
\citep{Astropy-Collaboration:2013}.
% This work used the Extreme Science and Engineering Discovery Environment
% \citep[XSEDE;][]{Towns:2014}, which is supported by National Science Foundation
% grant number ACI-1053575.

\bibliographystyle{apj}
\bibliography{refs}

\end{document}
